---
title: "Week5 Data Wrangling Demo"
author: "Mudong"
date: "February 11, 2020"
output: html_document
---

# Load data
```{r}
#install.packages("Lock5Data")
library(Lock5Data)
library(tidyverse)
library(ggplot2)
```

## data(), View(), help()
### HappyPlanetIndex

```{r}
# Should not write these command at code chunk, they should in console because they will take times to knit
#View(HappyPlanetIndex)
#help("HappyPlanetIndex")
```
To show the first few rows of the data
```{r}
head(HappyPlanetIndex)
HappyPlanetIndex %>%
  head()
```
To show the last few rows of the data

```{r}
tail(HappyPlanetIndex)
```

Note you have to use these command to familiar with data first, and then think about plots to visualize the data. This process is called Exploratory Data Analysis (EDA).

### Minneapolis2013
```{r}
library(DataComputing)
head(Minneapolis2013)
```

# Data Wrangling
## Bar plot
Aggregate the vote result for each candidate
```{r}
VoteResults <- 
  Minneapolis2013 %>%
  group_by(First) %>%
  summarise(votes = n())

head(VoteResults)
```

Plot bar plots. h
